\section{First Assignment}
\label{sec:problemI}
The purpose of this assignment was to implement an exact algorithm to solve the problem using the CPLEX API.
Before calling the \verb|solve| function
it is necessary to set up the CPLEX environment and problem, i.e. to deliver the variables and constraints to CPLEX. This is done by means of the \verb|setupLP| function.
Since we are interested (only) in the objective function and the $y_{ij}$ variables, i.e. if the arc from $i$
to $j$ is used, the function takes
an additional\footnote{with respect to the given skeleton.} parameter,  \verb|mapY|. This is used to
retrieve from the CPLEX API the values of those variables, if the option  \verb|--print| is enabled.
The set up phase consists in generating the variables and the constraints and passes them to CPLEX.

\paragraph{Variables generation}
The variables of the problem are $x_{ij}$ and $y_{ij}$ $\forall i,j \in N$.
In order to try to render the solution more efficient the program does not pass
to CPLEX the variables with index $(i,i)$. Indeed these arcs can be ignored, because
they will never be used.



\paragraph{Note about particular Data-Structures} In order to render the reference to the generated variables easier
during the constraints generation phase, I used two bi-dimensional vectors \verb|mapX| and \verb|mapY|, that 
associate to the index $(i,j)$ the corresponding CPLEX variables' index.
%contains in position $ij$ the corresponding CPLEX-variable index. 
These data-structures are filled during the variables generation phase.

The maps are perfect squares ($N\times N$), but the entries in position $(i,i)$ are not delivered to CPLEX.
The advantage of using this approach is that $2\times N$ variables are spared ($N$ for $x$ and $N$ for $y$) and the constraints
contain less variables.
The drawback is evident, when one write a function that reads the variables back from CPLEX with this configuration. He easily realizes
that it is challenging and hard to read.
You can check it out in the \verb|fetch_and_print_y_variables| function.
Since this functionality was not requested explicitly by the assignment,
this drawback can be ignored. Thus this approach is worth the effort.



